Instructions for developing new pages for the MarineOmics webpage

### 2023-06-02 ADMIN_01_submissions_instructions.Rmd
fixed typo on submissions instructions and made a bunch of progress on the QTL tutorial

To insert an image, you need the image file to also be uploaded to the
Github repositority. We store the images hosted on the website in the
`images/` folder. For any image, please make sure you have permission to
share the image and that it is appropriately cited.

>>>>

To insert an image, you need the image file to also be uploaded to the
Github repository. We store the images hosted on the website in each page's folder and call them accordingly. For any image, please make sure you have permission to
share the image and that it is appropriately cited.
